### 2023-05-17 application.tex
sections

\cite{DBLP:journals/acta/ValkJ85} showed from a VASS $V$ how to construct another VASS $V'$ that has the property...

>>>>

\cite{DBLP:journals/acta/ValkJ85} showed from a VASS $V$ and one of the 4 properties P, how to construct the maximal VASS $V'$ that has the property P which are exactly the maximal $X$-resilient VASS.
